l

### 2019-12-24 random/career_preparation/resume/resume.tex
go
resume update

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Chicago}
{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
\textbf{Santa Clara High School} \hfill \textbf{2017}
%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Julia, Bash, C\\
\textbf{Packages:}  PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas \\
\textbf{Spoken:} English, Hindi, Spanish

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab LSST Intern\hfill Jun 24 - Aug 31}\\
\textbullet{Researched the applications of neural differential equations to astronomy\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Technology/Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
\textbullet{Package to track odds and player data from a variety of sports and sources\\}
\textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
\textbullet{Example prediction models using TensorFlow, including classification and LSTM prediction models}
\begin{itemize}
\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, TensorFlow
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}

\begin{itemize}
\item \textbf{Technology/Tools:} Python, Gym, TensorFlow, TF-Agents
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/gym-sips
\end{itemize}

\section{COURSES}
\par
\normalfont{\textbullet{Algorithms}}
\normalfont{\textbullet{Discrete Math}}
\normalfont{\textbullet{Abstract Linear Algebra}}
\normalfont{\textbullet{Mathematical Logic}}
\normalfont{\textbullet{Inventing Interactive Devices}}
\normalfont{\textbullet{Electronics}}
\normalfont{\textbullet{Computer Systems}}
\section{ACTIVITIES}

\textbf{UCQuantum (.org)\hfill Aug 2019 - Now}\\
\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
\textbullet{We have 50 facebook group members and 10 active members}\\
\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
%-------------------------------------------------------------------------------

>>>>

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Chicago}
{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
\textbf{Santa Clara High School} \hfill \textbf{2017}

\section{COURSES}
\par
\normalfont{\textbullet{Algorithms}}
\normalfont{\textbullet{Discrete Math}}
\normalfont{\textbullet{Abstract Linear Algebra}}
\normalfont{\textbullet{Mathematical Logic}}
\normalfont{\textbullet{Inventing Interactive Devices}}
\normalfont{\textbullet{Electronics}}
\normalfont{\textbullet{Computer Systems}}

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Julia, Go, Bash, C\\
\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
\textbf{Spoken:} Fluent English. Classroom Hindi and Spanish

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun 24 - Aug 31 2019}\\
\textbullet{Researched the applications of neural differential equations to astronomy for the Large Synoptic Survey Telescope\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
\textbullet{Presented a poster of my work on Neural-ODEs at the 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
\textbullet{Created Python package to track odds and statistics for a variety of sports\\}
\textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
\textbullet{Trained TensorFlow win/loss classification and LSTM odds prediction neural network models on Sips data}\\
\textbullet{Wrote Flask app to visualize odds using Matplotlib}
\begin{itemize}
\item \textbf{Tools:} Python, Requests, Beautiful Soup, TensorFlow, Flask, Matplotlib
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}\\
\textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
\textbullet{Agent learns hedging strategies to mitigate risk}

\begin{itemize}
\item \textbf{Tools:} Python, Gym, TensorFlow, TF-Agents
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/gym-sips
\end{itemize}

\section{ACTIVITIES}

\textbf{UCQuantum (.org) - Founder/President}
\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
\textbullet{We have 50 facebook group members and 10 active members}\\
\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
%-------------------------------------------------------------------------------
